---
title: "Sessions"
---  


  
```{r, globalsettings, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"), cache.lazy = FALSE)
options(width = 100) 
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE, message=FALSE}
# install.packages("remotes")
#remotes::install_github("rlesur/klippy")
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```


----  

## Call for Panels 

Dear colleagues,

On Monday, June 17, 2024, the 24th Sociology Day takes place in Nijmegen. This year, the conference will be organized by the Sociology department of Radboud University, in collaboration with the Dutch Sociological Association (NSV) and the Flemish Association for Sociology (VVS).

As is annual tradition, the Sociology Day program consists of a mix of thematic panels. We would like to offer the opportunity to propose thematic panels to provide the opportunity for more specialized discussions and/or topics. This year there is a choice between a **presentation panel** and a round **table panel**. A full presentation panel consists of four paper presentations, preferably from at least two different universities or institutes. In a round table panel, a moderator will lead a discussion or exploration of a specific theme on the basis of (advanced) work by two to three researchers; different formats are possible. We are looking for a good mix of panels that are completely in Dutch and completely in English.

Panel proposals must be submitted no later than **Monday, January 29, 2024**. Please download and complete the form: `r xfun::embed_file('Call for panels formulier.docx', text = 'Call for panels form')`. Send this form to [dvds2024@nsv-sociologie.nl](mailto:dvds2024@nsv-sociologie.nl). 

The panel chairs will be informed of the approval of their panels prior to the *Call for Papers*.

Please feel free to distribute this call to colleagues and interested parties. If you have any questions, please do not hesitate to contact us at [dvds2024@nsv-sociologie.nl](mailto:dvds2024@nsv-sociologie.nl). 

Best wishes, 

Nella Geurts, Bas Hofstra, Klara Raiber, Jochem Tolsma en Ellen Verbakel



