---
title: "Sessions"
---  


  
```{r, globalsettings, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"), cache.lazy = FALSE)
options(width = 100) 
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE, message=FALSE}
# install.packages("remotes")
#remotes::install_github("rlesur/klippy")
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```


----  

### Sessions and abstracts

**General panels**

-	Bevolking 
-	Burgerschap 
-	Criminaliteit 
-	Cultuur 
-	Discriminatie
-	Etniciteit 
-	Familie
-	Gender 
-	Jeugd 
-	Klimaat 
-	Methode
-	Migratie 
-	Onderwijs 
-	Open sessie
-	Politiek 
-	Seksualiteit 
-	Sociale netwerken
-	Stratificatie / Klasse
-	Stad en stedelijkheid 
-	Theorie 
-	Werk 
-	Zorg / Gezondheid

----  

**Thematic panels**

*Mobilization on Display: Approaches to a Visual Sociology of Social Movements and Political Communication (NL or EN) - (open for submissions)*

Charlotte Bruns and Ofra Klein

With the rise and continuous influence of social media, visuals have become pivotal for political communication. The significance of visual elements is evident in the deliberate efforts of political parties, which enlist the expertise of professional graphic designers and advertising agencies to curate compelling visual content. Activist movements strategically choreograph actions to garner media attention, recognizing the potency of visuals in shaping public perception. Social media platforms facilitate the seamless upload of photos and live streaming during protests, rallies, and meetings, thereby empowering political actors and activists to construct a compelling visual narrative. Despite the growing impact of visuals in the political landscape, social science research has often overlooked their role. Scholars frequently neglect the nuanced ways in which visuals contribute to political communication and mobilization. 
This panel brings together scholars who work with visuals in their research. The aim is to discuss the heightened relevance of images in contemporary political discourse. By exploring different perspectives on visual politics, our discussion aims to shed light on the transformative potential of images, offering insights into their role in shaping political narratives and mobilizing public sentiment.

----

*Vluchtelingen in Nederland: hoe vinden zij hun weg in een nieuwe samenleving en welke rol speelt beleid hierin? (NL) - (open for submissions)*

Jaco Dagevos

In dit panel wordt onderzoek gepresenteerd over hoe vluchtelingen hun weg vinden in Nederland, met bijzondere aandacht voor beleidsfactoren. Deze sessie informeert over verschillende onderwerpen. We krijgen inzicht in de opzet en uitvoering van verschillende typen onderzoek (etnografisch, observaties, focusgroepen, kwantitatief) onder vluchtelingengroepen. Daarnaast leveren de papers een beeld van verschillende vormen van beleid waarmee vluchtelingen te maken krijgen en, voor zover mogelijk, staan we stil bij de gevolgen hiervan. Nederland heeft een nieuwe inburgeringswet en in een van de papers wordt onderzoek gepresenteerd over de ervaringen van deelnemers met deze wet. Statushouders doorlopen een asielprocedure doorlopen en hebben een inburgeringsplicht. Dit geldt niet voor Oekraïense vluchtelingen. Ook bestaan voor hen geen belemmeringen voor toetreding tot de arbeidsmarkt. Een vergelijking van de positie van beide groepen kan meer inzicht bieden in de  betekenis van deze verschillende vormen van beleid. In deze sessie wordt een voorstel voor dergelijk onderzoek gedaan. Een ander paper gaat in op de relatie tussen de taalverwerving van Syrische statushouders en het Nederlandse opvang- en inburgeringsbeleid, daarbij gebruikmakend van longitudinale gegevens voor de periode 2015-2022.

----

*Mantelzorg in context (NL) - (open for submissions)*

Alice de Boer and Marjolein Broese van Groenou

De steeds groter wordende vraag naar langdurige zorg en de ingrijpende hervormingen van het zorgsysteem zorgen voor onzekerheid onder Nederlandse burgers. Zij vragen zich af of zij zelf of hun naasten nog wel de zorg kunnen krijgen die zij nodig hebben. Deze situatie is vooral uitdagend voor diegenen die zelf hulp bieden aan hun naasten, ook wel mantelzorg genoemd. Voor de pandemie was een op de tien mantelzorgers overbelast door de hulp die zij bieden en de verwachting is dat de druk de komende jaren zal toenemen en waarschijnlijk ook de belasting die hiermee gepaard gaat. Dit komt onder andere doordat er meer ouderen zullen zijn die behoefte hebben aan hulp, terwijl er minder mensen zijn die hen hierbij kunnen helpen, en van deze mensen ook verwacht wordt dat ze participeren in betaald werk of opleiding. Meer inzicht in belangrijke determinanten en uitkomsten van mantelzorg zijn nodig om huidige en toekomstige mantelzorgers goed te kunnen ondersteunen. Het verlenen en krijgen van mantelzorg is een afweging op individueel niveau, maar deze afweging is altijd geplaatst in de context van de familie, het werk en de (buurt)gemeenschap en de samenleving. In deze sessie komen papers aan bod die naar mantelzorg in verschillende contexten nader bekijken. Twee papers gaan over gevers van mantelzorg in de context van werk en de buurt. Twee papers gaan over ontvangers van mantelzorg, met aandacht voor het sociale netwerk en het welbevinden van de zorgontvanger.  

----

*Sociology of Emotions (NL or EN) - (open for submissions)*

Aurélie Van de Peer and Mischa Dekker

While early scholarship on collective behavior tended to consider emotions solely through the prism of biology and contrasted them with rationality, the cultural turn in the social sciences brought attention to the cultural dimension of emotions. This body of work has emphasized that emotions are not simply biological reflexes nor experiential states that arise in a social vacuum; emotions are shaped by cultural understandings, norms, and processes of politicization. 

This panel welcomes papers that explore the role of emotions in any domain of social life (from education to culture, from law to media), including professional and private settings, online interactions, activism, and policymaking. We are interested in papers that address the intersectional dimensions of emotion: how are the ways in which people experience emotions informed by their race, class, and gender? And how do the ways emotional expressions are interpreted by groups of people vary across these lines and across various localized cultural settings? 

Moreover, the panel seeks to consider how emotions inform our understanding of gendered, racialized, and class-based inequalities. We welcome work that addresses the productive and inhibitive roles of emotions, encompassing both positively (happiness, pride, hope) and negative felt (shame, guilt, apprehension) emotions, as well as their impact on collective action, including activism and policy implementation.

Finally, this panel welcomes papers that aim to advance the theoretical aspects of sociology of emotions, for instance, by fleshing out the convergences and divergences with various humanities-inclined traditions in emotion studies. 

----

*Prejudice, racism and exclusionary reactions towards ethnic and religious minorities (NL or EN) - (open for submissions)* 

Marcel Coenders and Michael Savelkoul

Against the backdrop of increasing ethnic and cultural diversity and growing concerns of polarization in public and political discourse on migration and diversity related issues, it is crucial to understand the patterns and antecedents of prejudice, racism and exclusionary reactions towards different ethnic and religious minorities and across different domains or contexts. This panel will bring together researchers on prejudice, racism, and exclusionary reactions, tackling these issues from various perspectives, theoretical backgrounds and methods. We welcome empirical studies and innovative theoretical perspectives of patterns and antecedents of prejudice, racism and exclusion within or across different social domains and contexts. We are particularly interested in papers that examine temporal aspects of prejudice, racism and exclusion and address their individual and contextual patterns and determinants. Among others, we welcome papers that investigate prejudice, racism and exclusion towards specific minority groups and/or across different minority groups. Additionally, we welcome papers that address the manifestation of prejudice, racism, and exclusion within specific social domains and settings (e.g. schools, neighborhoods, and organisations) and how challenges of increasing diversity are perceived and addressed within these specific contexts. Finally, we welcome papers that study the role of policies aimed at combatting discrimination and fostering integration, equity and inclusion. 

----

*Political Sociology (NL of EN) - (open for submissions)*

Willem de Koster, Marcel Lubbers, and Niels Spierings

This panel is open for quantitative, qualitative or mixed-methods sociological research on socio-political attitudes and political participation, both inside institutional politics (e.g. voting behaviour) and outside formal institutions (e.g. protesting). Presentations on political polarization, support for certain political attitudes, non-voting or specific voting preferences can, for instance, be part of this panel. Selected submissions may focus on differences in these outcomes between social classes, educational categories, genders, ethnic groups or other differences in relation to the social and political context. It offers a platform at the Dag van de Sociologie to bring together sociologists interested in the study of politics.

----

*The Low Countries in Comparative Perspective: Results from International Surveys (EN) - (open for submissions)* 

Aat Liefbroer and Tim Reeskens


The Netherlands (and Belgium) participate in a number of international surveys. The European Social Survey (ESS), the European Value Study (EVS) and the International Social Programme (ISSP) focus on differences and trends in attitudes and values across Europe. The Generations and Gender Survey (GGS) focusses on changes in demographic and family behaviours. The Survey of Health, Aging and Retirement in Europe (SHARE) studies social change among older adults. In the Netherlands, all these surveys participate in and are funded by ODISSEI.
The aim of this session is to showcase research that can be done with these international surveys. In each presentation, comparative research based on one or more of these studies is presented. Focus of every presentation is to examine how The Netherlands (and Belgium) fare compared to other countries and to reflect on reasons for similarities and differences between the Low Countries and other parts of Europe.

----

*Ethnic, racial and religious discrimination: experimental designs and methodological innovations (EN)*

Valentina Di Stasio and Stefanie Sprong

In the past decade, a growing number of studies have relied on experimental methods to capture sensitive issues, such as discrimination on grounds of ethnicity, race and religion. Through a random allocation of ethnic and religious cues to fictitious applications (field experiments) or vignette-based scenarios (survey experiments), researchers have provided convincing evidence that members of minority groups face discrimination in the employment and housing sectors. In this panel, we discuss how aspects of the experimental design can influence the results obtained from field and survey experiments. 
The four studies included in the panel employ innovative methodological approaches that allow the authors to capture processes so far understudied, such as selective information acquisition from crucial gatekeepers (e.g. employers) or cumulative discrimination across life domains. In particular: Paper 1 extends the typical design of correspondence tests to the study of indirect discrimination in access to childcare; Papers 1 and 2 highlight the importance of pretesting experimental stimuli; Paper 3 introduces a novel technique (the click-to-reveal design) to minimize social desirability bias from respondents; Paper 4 reviews the operationalization choices made in previous research and their impact on the level of discrimination found in correspondence tests.

----

*Social Inequalities in International Higher Education (EN)*

Christof van Mol and Tijmen Weber

Higher education is rapidly internationalizing, but social inequalities in international higher education are still poorly understood. Nevertheless, the individual characteristics of students in terms of socio-economic background, gender, ethnicity, age, etc. can have a significant influence whether they take part in and benefit from internationalizing activities. Furthermore, on the country level, there are important differences in how far institutions are able to successfully internationalize and attract international students, and how socially inclusive they are. Understanding inequalities in international higher education is becoming increasingly important as higher education institutions are increasingly developing inclusive internationalization policies, which should be evidence-based. This panel presents a series of papers where inequalities in international higher education are highlighted, and their causes and consequences are discussed.    

----

*Sociology of Music I: Audiences and Tastes (EN)*

Pauwke Berkers and Julian Schaap

Sociological interest in music dates back to the birth of the sociological discipline, evidenced in the works of Max Weber, W.E.B. DuBois, and Georg Simmel. Contemporary cultural sociologists (Pierre Bourdieu, Howard Becker, Richard Peterson and others) have extensively studied music to address classic sociological issues as social inequality and cohesion. Indeed, Bourdieu famously argued that “nothing more clearly affirms one’s ‘class,’ nothing more infallibly classifies, than tastes in music” (1984:18). In their article in the Annual Review of Sociology, William G. Roy and Timothy J. Dowd (2010) demonstrate this wider sociological salience of the study of music, and show how it intersects with central sociological questions on social and social inequality and distinctions. 

This panel consists of four papers which each contribute – theoretically, methodologically and empirically – to a better understanding of these key issues in the sociology of music. All papers emphasize the consumption of music, from focusing on arts participation (Calkins et al.) to interactions between musicians and audiences (Vandenberg and Dalla Chiesa) and from nightlife visitors (Hermans) to concert goers (Peters et al.). Calkins et al. take a classical Bourdieu-inspired topic – breadth of tastes – and add the dimension of race/ethnicity. Vandenberg and Dalla Chiesa look at the traditional practices of busking in the online age. Hermans examines how young, white, cisgender, and straight men negotiate masculinity in inclusive nightlife spaces. Finally, Peters et al. measure physiological and social well-being amongst concert visitors.

----

*Sociology of Music II: Audiences and Gatekeepers (EN)*

Pauwke Berkers and Julian Schaap

Sociological interest in music dates back to the birth of the sociological discipline, evidenced in the works of Max Weber, W.E.B. DuBois, and Georg Simmel. Contemporary cultural sociologists (Pierre Bourdieu, Howard Becker, Richard Peterson and others) have extensively studied music to address classic sociological issues as social inequality and cohesion. Indeed, Bourdieu famously argued that “nothing more clearly affirms one’s ‘class,’ nothing more infallibly classifies, than tastes in music” (1984:18). In their article in the Annual Review of Sociology, William G. Roy and Timothy J. Dowd (2010) demonstrate this wider sociological salience of the study of music, and show how it intersects with central sociological questions on social and social inequality and distinctions. 

This panel consists of four papers which each contribute – theoretically, methodologically and empirically – to a better understanding of these key issues in the sociology of music. All papers emphasize the production of music, focusing musicians and bookers (Berkers & Wijngaarden), nightclub promotors (Koren), music managers (Calkins et al.), and musicians and policymakers (Mogoș). Yet, whereas Mogoș takes a historical approach, the other papers address the contemporary (Dutch) music industry. Berkers and Wijngaarden make an empirical contribution to studies of the gender pay gap in the cultural and creative industries, drawing on actual live concert fees. Koren draws on interviews with musical professional to make a methodological contribution. Calkins et al. have studied the understudied professional group of music managers. And finally. Mogoș sheds light on societal transitions through studying musicians and policymakers.

----

**Roundtables**


*Bring the mountain to us - sociology for sustainability scientists (EN or NL) - (open for submissions)*

Carien Moossdorff

Sustainability scientists need and want sociological theory and insights to help provide theoretical grounding for societal change processes towards a more sustainable future. As a sociological research group in a sustainability department, we have been getting a lot of positive responses from colleagues in the department, at sustainability conferences, and among stakeholders in the field. 

However, colleagues in the field of sustainability seem to have trouble finding sociology until we present it to them. This leads us to questions like: What is our responsibility as sociologists to share our theory? How do we retain the nuances of our field while presenting our insights in an accessible way? How, when, and why should we choose to be normative in our statements? 

During this roundtable, we will engage in a discussion on the opening up of sociology to sustainability researchers. We will bring in speakers from academic sociology, sustainability sciences, and the applied sustainability field. We are looking to have a freeform discussion with all participants on the topic of bringing sociology to sustainability fields.

----

*Collecting ethno-religious minority survey data in times of survey fatigue (EN)*

Niels Spierings and Nella Geurts

The Netherland have a long and strong tradition when it comes to collection survey data, both generally and using oversampling to assess the position of and attitudes among ethno-religious minorities, migrant citizens and their children. However, developments in survey collection (e.g. shift to online), in costs (AVG; monetary) and in society at large (e.g. the politicization on ethno-religious minorities; survey fatigue; covid-19 pandemic; institutional racism by the Dutch government) have lead to new realities and challenges. Maybe not surprisingly, several recent data collections among ethno-religious minorities have struggled to meet response targets and questions have arisen regarding selection and response biases. In this roundtable we tackle this issue.

Several scholars with recent experiences collecting survey data among ethno-religious minorities team up to (a) discuss the problems they run into and above all (b) what is needed to overcome these challenges. This discussion will be focused on real-life science. The focus is not on what would be ideal, but what can be done in the here and now or which steps are needed and can be taken to get closer to an ideal. 

Each speaker will very briefly start the round table by highlighting a main challenge after which this list is discussed in terms of solutions. The public will also be invited to contribute solutions and as a result of the round table we hope to work towards a roadmap. 



